THE FUNDAMENTAL CONNECTIONS BETWEEN CLASSICAL HAMILTONIAN MECHANICS, QUANTUM MECHANICS \\ AND INFORMATION ENTROPY

### 2019-10-16 Proceedings/2019-Quantum2019/CarcassiQuantum2019Proceedings.tex
Adding bibliography

\section{Introduction}
In a previous work\cite{Carc1} we identified a small set of physical assumptions from which classical and quantum particle mechanics can be rederived. By assumptions here we mean simplifying conditions that our system is supposed to satisfy under the processes under study. Our work differs from others\cite{PhysRevA.84.012311} CITE in that the starting points are physical assumptions about the system being studied (e.g whether the parts can be studied or whether the evolution is deterministic) and not information theoretic or abstract mathematical  considerations. It is also different in that both classical and quantum cases are derived on equal footing. That is, we have identified a single point where one assumption leads to the classical case while another leads to the quantum system.

@@

It turns out this distribution is the product of two Gaussian distributions
\begin{equation}
\rho(q,k) = \frac{1}{2\pi\sigma_q\sigma_k} e^{- \frac{(q - \mu_q)^2}{2 \sigma_q^2}} e^{- \frac{(p - \mu_p)^2}{2 \sigma_p^2}}
\end{equation}
with information entropy
\begin{equation}
I_G = \ln (2 \pi e \sigma_q \sigma_k).
\end{equation}
Since this is the distribution that minimizes the spread, during the evolution we have
\begin{equation}
\sigma_q \sigma_k \leq \frac{e^{I_0}}{2 \pi e}
\end{equation}
where $I_0$ is the initial information entropy. This classical uncertainty relationship is reminiscent of the quantum uncertainty relationship in both the form and the fact that the equality holds for the Gaussian packets. The analogy can be made stronger with a few extra conditions as described in Ref\cite{Carc1}. What we want to show here is the connection between this uncertainty relationship, information entropy, deterministic and reversible evolution and the difference in reducibility between a classical and a quantum system.

>>>>

\section{Introduction}
In a previous work\cite{Carc1} we identified a small set of physical assumptions from which classical and quantum particle mechanics can be rederived. By assumptions here we mean simplifying conditions that our system is supposed to satisfy under the processes under study. Our work differs from others, see for example Refs.~\citenum{PhysRevA.84.012311,QLogicReview,Hardy:2001jk,ludwig_hein_2013}, in that the starting points are physical assumptions about the system being studied (e.g. whether the parts can be studied or whether the evolution is deterministic) and not information theoretic or abstract mathematical considerations. It is also different in that both classical and quantum cases are derived on equal footing. That is, we have identified a single point where one assumption leads to the classical case while another leads to the quantum system.

@@

It turns out this distribution is the product of two Gaussian distributions
\begin{equation}
\rho(q,k) = \frac{1}{2\pi\sigma_q\sigma_k} e^{- \frac{(q - \mu_q)^2}{2 \sigma_q^2}} e^{- \frac{(p - \mu_p)^2}{2 \sigma_p^2}}
\end{equation}
with information entropy
\begin{equation}
I_G = \ln (2 \pi e \sigma_q \sigma_k).
\end{equation}
Since this is the distribution that minimizes the spread, during the evolution we have
\begin{equation}
\sigma_q \sigma_k \leq \frac{e^{I_0}}{2 \pi e}
\end{equation}
where $I_0$ is the initial information entropy. This classical uncertainty relationship is reminiscent of the quantum uncertainty relationship in both the form and the fact that the equality holds for the Gaussian packets. The analogy can be made stronger with a few extra conditions as described in Ref.~\citenum{Carc1}. What we want to show here is the connection between this uncertainty relationship, information entropy, deterministic and reversible evolution and the difference in reducibility between a classical and a quantum system.
